### 2015-10-20 doc/notebook/Archaeal_data_acquisition.Rmd
Fix how rendered to markdown
Fix bullet list formatting

@@

opts_chunk$set(eval = FALSE)
opts_chunk$set(echo = FALSE)
```

@@

To get good sequences...
* Go to search window
* Set Search_Fields to "ARB_color" and use "1"; click on the equal sign to make it not equal
* Hit Mark Listed, Unmark Rest button (N=1493493)
* The problem with the taxonomies is that the sequences don't all have taxonomies. Need to figure
    out which taxonomy to base the analysis on. Do the following searches...
    * ARB_color != 1 & tax_rdp == "*Archaea*" (N=40288)
    * ARB_color != 1 & tax_greengenes == "*Archaea*" (N=19795)
    * ARB_color != 1 & tax_slv == "*Archaea*" (N=17641)
    * ARB_color != 1 & tax_embl == "*Archaea*" (N=44574)
    * ARB_color != 1 & (tax_rdp | tax_greengenes | tax_embl | tax_slv) (N=46387 )

@@

Now we need the taxonomy information.
* Go Tree -> NDS
* Click "name", "acc", "tax_rdp". The "tax_rdp" field should have 250 characters
* Unclick everything else
* Click "Close"
* Go File->Export->Export fields
* Set the file name to "archaea.taxonomy" and Column output to "TAB separated"
* Click "SAVE"

>>>>

---
output: md_document
---

@@

opts_chunk$set(eval = FALSE)
opts_chunk$set(echo = TRUE)
```

@@

To get good sequences...

* Go to search window
* Set Search_Fields to "ARB_color" and use "1"; click on the equal sign to make it not equal
* Hit Mark Listed, Unmark Rest button (N=1493493)

The problem with the taxonomies is that the sequences don't all have taxonomies. Need to figure out which taxonomy to base the analysis on. Do the following searches...

* ARB_color != 1 & tax_rdp == "*Archaea*" (N=40288)
* ARB_color != 1 & tax_greengenes == "*Archaea*" (N=19795)
* ARB_color != 1 & tax_slv == "*Archaea*" (N=17641)
* ARB_color != 1 & tax_embl == "*Archaea*" (N=44574)
* ARB_color != 1 & (tax_rdp | tax_greengenes | tax_embl | tax_slv) (N=46387 )

@@

Now we need the taxonomy information.

* Go Tree -> NDS
* Click "name", "acc", "tax_rdp". The "tax_rdp" field should have 250 characters
* Unclick everything else
* Click "Close"
* Go File->Export->Export fields
* Set the file name to "archaea.taxonomy" and Column output to "TAB separated"
* Click "SAVE"

### 2015-10-20 doc/notebook/Bacterial_data_acquisition.Rmd
Fix how rendered to markdown
Fix bullet list formatting

To get good sequences...
* Go to search window
* Set Search_Fields to "ARB_color" and use "1"; click on the equal sign to make it not equal
* Hit Mark Listed, Unmark Rest button (N=1493493)
* The problem with the taxonomies is that the sequences don't all have taxonomies. Need to figure
    out which taxonomy to base the analysis on. Do the following searches...
    * ARB_color != 1 & tax_rdp == "*Bacteria*" (N=1324558)
    * ARB_color != 1 & tax_greengenes == "*Bacteria*" (N=1123144)
    * ARB_color != 1 & tax_slv == "*Bacteria*" (N=426917)
    * ARB_color != 1 & tax_embl == "*Bacteria*" (N=1207210)
    * tax_rdp | tax_greengenes | tax_embl | tax_slv (N=1376910)

@@

Now we need the taxonomy information.
* Go Tree -> NDS
* Click "name", "acc", "tax_rdp". The "tax_rdp" field should have 250 characters
* Unclick everything else
* Click "Close"
* Go File->Export->Export fields
* Set the file name to "data/mothur/bacteria.taxonomy" and Column output to "TAB separated"
* Click "SAVE"

>>>>

To get good sequences...

* Go to search window
* Set Search_Fields to "ARB_color" and use "1"; click on the equal sign to make it not equal
* Hit Mark Listed, Unmark Rest button (N=1493493)

The problem with the taxonomies is that the sequences don't all have taxonomies. Need to figure out which taxonomy to base the analysis on. Do the following searches...

* ARB_color != 1 & tax_rdp == "*Bacteria*" (N=1324558)
* ARB_color != 1 & tax_greengenes == "*Bacteria*" (N=1123144)
* ARB_color != 1 & tax_slv == "*Bacteria*" (N=426917)
* ARB_color != 1 & tax_embl == "*Bacteria*" (N=1207210)
* tax_rdp | tax_greengenes | tax_embl | tax_slv (N=1376910)

@@

Now we need the taxonomy information.

* Go Tree -> NDS
* Click "name", "acc", "tax_rdp". The "tax_rdp" field should have 250 characters
* Unclick everything else
* Click "Close"
* Go File->Export->Export fields
* Set the file name to "data/mothur/bacteria.taxonomy" and Column output to "TAB separated"
* Click "SAVE"
